my title

### 2024-12-02 paper/paper.qmd
update model set-up

---
title: ""
subtitle: ""
author: 
  - Yawen Tan
thanks: "Code and data are available at: [https://github.com/YawennnnnnTan/Analysis-of-Diamond-Price]"
date: today
date-format: long
abstract: ""
format: pdf
number-sections: true
bibliography: 
  - references .bib
toc: true
---

@@

## Measurement {#sec-measurement}
钻石颜色等数据是如何得出的
然后提到数据集是如何得出的

@@

## Outcome Variable {#sec-outcomevar}

@@

## Data preparation
包括如何处理reponse来符合gamma。详细请见appendix

@@

Define \( y_i \) as the price of the \( i \)-th diamond. Predictors include:

\begin{itemize}
    \item \( x_{1i} \): The carat size of the diamond (in carats).
    \item \( x_{2i} \): The color grade of the diamond (categorical).
    \item \( x_{3i} \): The cut grade of the diamond (categorical).
    \item \( x_{4i} \): The clarity grade of the diamond (categorical).
\end{itemize}

**Model Structure**:
1. **Response Distribution**:  
   \[
   y_i \mid \mu_i, \phi \sim \text{Gamma}(\mu_i, \phi),
   \]
   where \( \mu_i \) is the mean price and \( \phi \) is the dispersion parameter.

2. **Link Function**:  
   \begin{align}
   \log(\mu_i) &= \beta_0 + \beta_1 x_{1i} 
   + \sum_{j} \beta_{2j} \cdot \text{color}_{ij} \nonumber \\
   &\quad + \sum_{k} \beta_{3k} \cdot \text{cut}_{ik} 
   + \sum_{l} \beta_{4l} \cdot \text{clarity}_{il}.
   \end{align}
   - \( \beta_0 \): Intercept term.  
   - \( \beta_1 \): Effect of carat size.  
   - \( \beta_{2j}, \beta_{3k}, \beta_{4l} \): Effects of color, cut, and clarity, respectively.

3. **Mean Price**:  
   \begin{align}
   \mu_i &= \exp\left(\beta_0 + \beta_1 x_{1i} 
   + \sum_{j} \beta_{2j} \cdot \text{color}_{ij} \right. \nonumber \\
   &\quad \left.+ \sum_{k} \beta_{3k} \cdot \text{cut}_{ik} 
   + \sum_{l} \beta_{4l} \cdot \text{clarity}_{il}\right).
   \end{align}

## Model justification{#sec-justification}
为什么选择glm，以及为什么选择gamma，因为data section 里reponse符合分布
We expect a positive relationship between the size of the wings and time spent aloft. In particular...

@@

cat("AIC:", aic_value, "\n")
cat("BIC:", bic_value, "\n")
```

>>>>

---
title: "my title"
subtitle: "subtitle"
author: 
  - Yawen Tan
thanks: "Code and data are available at: [https://github.com/YawennnnnnTan/Analysis-of-Diamond-Price]"
date: today
date-format: long
abstract: "4 sentence"
format: pdf
number-sections: true
bibliography: 
  - references .bib
toc: true
---

@@

@@

```
## Measurement {#sec-measurement}

@gia_4cs illustrates the measurement of diamond features. Color is conducted by comparing the diamond against GIA’s master stones (graded from D to Z) under controlled lighting and background conditions, as light sources significantly affect appearance. At least two graders assess each diamond's color, with additional graders involved if discrepancies arise, until a consensus is reached. Clarity is performed under 10x magnification in standard observation conditions, where the grader examines internal and external characteristics, documenting inclusions, blemishes, or treatments such as laser drilling or fracture filling. Cut utilizes high-precision instruments to measure cutting proportions, angles, symmetry, and polish quality, following international standards set by organizations like GIA or AGS, with grades such as Excellent and Very Good. Carat size is determined using highly accurate electronic microbalances, capable of measuring to five decimal places, or one ten-thousandth of a carat, complemented by optical devices to assess the diamond’s proportions, dimensions, and facet angles.

## Outcome Variable: Price {#sec-outcomevar}

@@

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

@@

Define $y_i$  as the price of the i th diamond. Predictors include:

-   $x_{1i}$: The carat size of the diamond (in carats).
-   $x_{2i}$: The color grade of the diamond (categorical).
-   $x_{3i}$: The cut grade of the diamond (categorical).
-   $x_{4i}$: The clarity grade of the diamond (categorical).

1. **Response Distribution**: 
   \begin{align}
   y_i |\mu_i, \phi \sim \text{Gamma}(\mu_i, \phi),
   \end{align}
   where $\mu_i$ is the mean price and $\phi$ is the dispersion parameter.

2. **Link Function**:

   \begin{align}
   \log(\mu_i) &= \beta_0 + \beta_1 x_{1i} + \sum_{j} \beta_{2j} \cdot \text{color}_{ij} \nonumber \\
   &\quad + \sum_{k} \beta_{3k} \cdot \text{cut}_{ik} + \sum_{l} \beta_{4l} \cdot \text{clarity}_{il}.
   \end{align}
   - $\beta_0$: Intercept term.  
   - $\beta_1$: Effect of carat size.  
   - $\beta_{2j}$, $\beta_{3k}$, $\beta_{4l}$: Effects of j color, k cut, and l clarity, where j includes: D,E,F,G,H,I,J,K; k includes: Ideal, Excellent, Very Good, Good; l include IF, VVS1, VVS2, VS1, VS2, SI1, SI2.

3. **Mean Price**:  
   \begin{align}
   \mu_i &= \exp\left(\beta_0 + \beta_1 x_{1i} + \sum_{j} \beta_{2j} \cdot \text{color}_{ij} \right. \nonumber \\
   &\quad \left.+ \sum_{k} \beta_{3k} \cdot \text{cut}_{ik} + \sum_{l} \beta_{4l} \cdot \text{clarity}_{il}\right)
   \end{align}

## Model justification{#sec-justification}
为什么选择glm，以及为什么选择gamma，因为data section 里reponse符合分布

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

@@
